Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
authors

author-information:
    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254**, and Michael C. Frank}

@@

author-note:
    "*These authors contributed equally. **Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@

100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%

>>>>

author-information:
    - \author{Robert X. D. Hawkins*, Eric N. Smith*, the Psych 254 Students**, and Michael C. Frank}

@@

author-note:
    "*These authors contributed equally and are listed alphabetically. **Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."

@@
